Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-16 main.tex
Updates from Overleaf

Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content (van Dokkum et al. 2018) to their globular cluster populations (Danieli et al. 2022). A central question related to UDGs is what physical mechanisms are responsible for their formation. Before we can answer this question, it is important to reliably determine in what environment they live.
Past UDG studies focused on rich galaxy groups and clusters (e.g., Yagi et al. 2016, Zatrisky et al. 2019), which provides distance information. Although UDGs are also found in field environments (Prole et al. 2019, Tanoglidis et al. 2021, Kadowaki et al. 2021), most studies of field UDGs lack distances and thus are statistical in nature. UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see Rom\'{a}n et al. 2019, Prole et al. 2019). This suggests that environment plays a crucial role in the formation and quenching of UDGs. Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, Benavides et al. 2021). It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end. A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.

The best knowledge we have about dwarf galaxies at the very faint end was derived from systems in the Local Volume (e.g., Simon 2019, Carlsten et al. 2021). To better compare UDGs with other dwarf systems, we turned to looking for UDGs in the vicinity of Milky Way analogs at $0.01 < z < 0.04$. Until now, there are only $\sim 10$ confirmed UDGs associated with MW analogs (Cohen et al. 2018, Mao et al. 2021). The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored. With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.

Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep). In order to study the formation and evolution of UDGs in low-density environments, we first select host galaxies at $0.01 < z < 0.04$ with Milky-Way masses ($10.2 < \log M_*/M_\odot < 11.2$) in the NASA-Sloan Atlas. We matched our HSC LSBGs catalog with the MW-like hosts catalog. We assign an LSBG to a host if their angular separation is smaller than the projected virial radius of the host. Then we select a UDG sample by requiring the $g$-band average surface brightness within the effective radius\footnote{This surface brightness threshold is equivalent to $\mu_0(g) > 24.0\ \mathrm{mag\ arcsec^{-2}}$ (van Dokkum et al. 2015) for S\'{e}rsic model with $n=1$.} $\overline{\mu_e} > 24.4\ \mathrm{mag\ arcsec^{-2}}$ and effective radius $R_e > 1.5$ kpc, under the assumption that all matched LSBGs are physically associated with the hosts. Following these steps, we have identified $\sim$ 250 UDG candidates to be associated with Milky Way-like hosts in projection. They span a wide range of surface brightness, size, color, nucleation, and host properties, making this sample ideal for studying UDG spatial distributions, quenched fractions, mass-size relations, nucleation fractions, and their dependence on host properties.

@@

As mentinoed above, we only model sources within the bounding box of the target. However, scattered lights from nearby bright stars and galaxies could bias the modeling within the bounding box. We match our field with the GAIA catalog and mask out stars outside of the bounding box. Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.

@@

\subsection{Size distribution}
\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{size_distribution.pdf}
	}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure*}

The size distribution of UDGs is an important topic since it has been used to test various UDG formation scenario \citep[e.g.,][]{Amorisco2016,vdBurg2017}. In this section, we calculate the size distribution of our UDG and UPG sample. We split UDGs into 10 bins in $\log r_e$ with a bin width of 0.06 dex. Then we calculate the number of UDGs per bin .

We also take the measurement error in $r_e$ into account.

\subsection{Spatial distribution}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{radial_distribution.pdf}
	}
    \caption{Caption}
    \label{fig:radial_distribution}
\end{figure*}

\subsection{Quenched fraction}\label{sec:quench}

@@

\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.

When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish?

This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.

@@

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
	}
    \caption{Caption}
    \label{fig:qfrac_dist2host}
\end{figure*}

\section{Discussion and Conclusion}
Scenarios:
1. violent environmental effects: radial orbits, back-splash both explain large size and quenching. But according to Bernavidis et al, the quenched fraction drops with increasing mass.

@@

\section*{Acknowledgment}
JL is grateful for discussions with XXX. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.

@@

\vspace{1em}
\software{\href{http://www.numpy.org}{\code{NumPy}} \citep{Numpy},
          \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy}, \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
          \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
          \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}, \href{https://github.com/dr-guangtou/unagi}{\code{unagi}}.
          }

@@

\section{Spergel profiles}\label{ap:spergel}

@@

To study the correspondence between \sersic{} and Spergel profiles, we generate \sersic{} profiles with different \sersic{} indices, and try to fit Spergel profiles to \sersic{} ones. The \sersic{} index ranges from $n=0.5$ to $n=4.5$, and both profiles are normalized using $r_e$. For each \sersic{} profile, we calculate the total luminosity $L_0$ according to \eqref{eq:sersic_lum} and plug it into the Spergel profile \eqref{eq:spergel} as a fixed value. Therefore, only the Spergel index $\nu$ is allowed to vary during the fitting. The best-fit Spergel index $\nu$ as a function of \sersic{} index $n$ is shown in the left panel of Figure \ref{fig:spgl_calib}. As two examples, we show two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) in the right panel. A Spergel profile with $\nu=0.5$ is exactly an exponential profile with $n=1$. The de vaucouleurs profile \citep{deVaucouleurs1948} with $n=4$ can be approximated by a Spergel profile with $\nu=-0.74$.

@@

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=0.75\linewidth]{spergel_sersic_calib.pdf}
	}
    \caption{The correspondence between the \sersic{} profile \eqref{eq:sersic} and the Spergel profile \eqref{eq:spergel}. We fit a Spergel profile to \sersic{} while fixing the total luminosity and half-light radius. The left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$. In the right panel, two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) are shown. Spergel profile approximates \sersic{} well for small \sersic{} indices.  
    }
    \label{fig:spgl_calib}
\end{figure*}

\section{Measurement Error}\label{ap:meas_error}

We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

>>>>

Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al. 2022). A central question related to UDGs is what physical mechanisms are responsible for their formation. Before we can answer this question, it is important to reliably determine in what environment they live.
Past UDG studies focused on rich galaxy groups and clusters \citep[e.g.,][]{Yagi2016,Zaritsky2019}, which provides distance information. Although UDGs are also found in field environments \citep{Prole2019,Tanoglidis2021,Kadowaki2021}, most studies of field UDGs lack distances and thus are statistical in nature. UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see \citealt{Roman2019,Prole2019}). This suggests that environment plays a crucial role in the formation and quenching of UDGs. Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, \citealt{Benavides2021}). It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end. A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.

The best knowledge we have about dwarf galaxies at the very faint end was derived from systems in the Local Volume \citep[e.g.,][]{Simon2019,CarlstenELVES2022}. To better compare UDGs with other dwarf systems, we turned to looking for UDGs in the vicinity of Milky Way analogs at $0.01 < z < 0.04$. Until now, there are only $\sim 30$ confirmed UDGs associated with MW analogs \citep{Cohen2018,SAGA-II,CarlstenELVES2022}. The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored. With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.

% Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep). In order to study the formation and evolution of UDGs in low-density environments, we first select host galaxies at $0.01 < z < 0.04$ with Milky-Way masses ($10.2 < \log M_*/M_\odot < 11.2$) in the NASA-Sloan Atlas. We matched our HSC LSBGs catalog with the MW-like hosts catalog. We assign an LSBG to a host if their angular separation is smaller than the projected virial radius of the host. Then we select a UDG sample by requiring the $g$-band average surface brightness within the effective radius\footnote{This surface brightness threshold is equivalent to $\mu_0(g) > 24.0\ \mathrm{mag\ arcsec^{-2}}$ (van Dokkum et al. 2015) for S\'{e}rsic model with $n=1$.} $\overline{\mu_e} > 24.4\ \mathrm{mag\ arcsec^{-2}}$ and effective radius $R_e > 1.5$ kpc, under the assumption that all matched LSBGs are physically associated with the hosts. Following these steps, we have identified $\sim$ 250 UDG candidates to be associated with Milky Way-like hosts in projection. They span a wide range of surface brightness, size, color, nucleation, and host properties, making this sample ideal for studying UDG spatial distributions, quenched fractions, mass-size relations, nucleation fractions, and their dependence on host properties.

@@

As mentinoed above, we only model sources within the bounding box of the target. However, scattered lights from nearby bright stars and galaxies could bias the modeling within the bounding box. We match our field with the Gaia catalog and mask out stars outside of the bounding box. Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.

@@

\subsection{Size distribution}\label{sec:size_distr}
\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{size_distribution.pdf}
	}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure*}

The size distribution of UDGs is an important topic since it has been used to test UDG formation scenarios \citep[e.g.,][]{Amorisco2016,vdBurg2017}. In this section, we calculate the size distribution of our UDG and UPG sample. First of all, we take the fake UDGs in random fields and calculate their size distribution as a proxy for background contamination, shown as the gray dots in the left panel of Figure \ref{fig:size_distribution}. For each host, we calculate the raw size distribution of the associated UDGs (black dots), and we multiply background size distribution by the virial area of the host and subtract it from the UDG size distribution (teal dots). Then we combine the UDG size distributions for all hosts together, and correct for completeness (red squares). Since the stellar masses of the hosts in our sample are quite similar, we do not weight each host according to their masses. The error shown in Figure \ref{fig:size_distribution} takes both Poisson error and the measurement error of size into account.

We find that the UDG size distribution roughly follows a power law. We fit a power law relation to our UDG size distribution and get $n\propto r_e^{-1.60\pm0.21}$. This is shallower than the power law presented in \citet{vdBurg2016} ($n\propto r_e^{-3.40\pm0.19}$) and \citet{vdBurg2017} ($n\propto r_e^{-2.71\pm0.33}$, shown as gray dash-dotted lines in Figure \ref{fig:size_distribution}). We also split the UDG sample based on their host stellar mass, but consistently find shallow power-laws with index $\sim -1.6$. \citet{vdBurg2016} studies large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep. Combined with our findings, it might be possible that dense environment produces more small UDGs. \jiaxuan{Have anything to do with tidal stripping? UDGs in denser environs are more stripped thus smaller?}

We also show the size distribution of UPGs in the right panel of Figure \ref{fig:size_distribution}. Unlike UDGs, we make the UPG sample by cutting through the 1.5$\sigma$ line above the mass-size relation. Therefore, for a given mass, many small UDGs are not in the UPG sample since their sizes are not extreme on the mass-size plane. As a consequence, the size distribution of UPG sample is suppressed at the smaller size end.

\subsection{Radial distribution}\label{sec:radial_distr}
Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers). In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment. \citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto \citep{Einasto1965} profile. In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.

We calculate the radial distribution as follows. For each host, we count the number of UDGs in each radial bin scaled by $R_{\rm vir}$ and calculate the number density within each radial annulus. We subtract the contribution of background contaminants based on the background contamination density (Sec. \ref{sec:bkg}) and the angular area occupied by the host. Then we average over all hosts and correct for the completeness, as shown in Figure \ref{fig:radial_distribution}. Red squares are the number of UDGs (UPGs) per radial bin, and the error includes Poisson error, background subtraction error, and completeness error. The radial distributions of both UDGs and UPGs turn over around $R=0.2\,R_{\rm vir}$. It is known that the detection can be more incomplete as it gets closer to the host due to the blending between UDG and the host galaxy outskirts and possible sky subtraction issues. Although we have corrected the completeness for each object based on their size and surface brightness, it is still possible that our completeness does not include the dependence on the distance to the host. As we mentioned above, it is also possible that UDGs and UPGs are depleted because of strong tidal interactions.

We fit the radial distributions of UDG (UPG) with the projected NFW and Einasto profiles at $R > 0.2 R_{\rm vir}$. The Einasto profile introduces an extra ``shape'' parameter $\alpha$ and has been argued to be a better description to the dark matter halo profiles \citep[e.g.,][]{Navarro2004,Gao2008,Navarro2010,Dutton2014}. Einasto profile also makes concentration estimates less sensitive to the radial range fitted. The best-fit NFW and Einasto profiles are shown in Figure \ref{fig:radial_distribution} as blue and red lines, respectively. The best-fit Einasto profile from \citet{vdBurg2016} is shown as the dashed gray line.

Compared with \citet{vdBurg2016}, there are more UDGs at smaller radial distances in our sample, thus the UDG radial distribution is more concentrated although we exclude $R < 0.2\ R_{\rm vir}$. Unlike \citet{vdBurg2016}, we find that both NFW and Einasto could describe the radial distribution of UDGs (UPGs) quite well. The concentration of the best-fit NFW profile is $c_{\rm NFW, UDG} = 10.1^{+6.5}_{-3.9}$ for UDGs and $c_{\rm NFW, UPG} = 10.9^{+8.9}_{-4.9}$ for UPGs. The best-fit Einasto profile has $\alpha_{\rm Ein, UDG} = 0.44^{+0.42}_{-0.22},\ c_{\rm Ein, UDG} = 3.30^{+2.07}_{-1.27}$ for UDGs and $\alpha_{\rm Ein, UPG} = 0.40^{+0.56}_{-0.23},\ c_{\rm Ein, UPG} = 3.55^{+3.63}_{-1.80}$ for UPGs. The radial distribution profiles of UDGs and UPGs are found to be very similar in shape. Our best-fit Einasto profiles have lower $\alpha$ and higher concentration compared with \citet{vdBurg2016} where $\alpha_{\rm Ein} = 0.92^{+0.08}_{-0.18},\ c_{\rm Ein} = 1.83^{+0.13}_{-0.12}$.

According to the concentration-mass relation of dark matter halos, the concentration of MW-like halo is $c_{\rm NFW} \sim 10$ \citep{Bullock2001,Duffy2008,Dutton2014}. Therefore, if assuming an NFW profile, the UDGs and UPGs follow the underlying dark matter distribution of the host. However, the Einasto shape parameter for a MW-like halo is $\alpha\sim 0.15$ at $z=0$ and its concentration $c\sim 8-10$. \citep{Gao2008,Dutton2014}. Comparing with this, the best-fit Einasto profiles for UDG (UPG) radial distribution have larger shape parameter $\alpha$ and smaller concentration $c$. We notice that the errors of the best-fit parameters are large due to the sample size and also the fact that concentration is most sensitive to data at smaller radial distances which are excluded in the analysis. Therefore, the UDG (UPG) radial distribution can be considered consistent with the dark matter distribution of the host. Nevertheless, a larger and more complete sample is needed to better constrain the radial distributions.

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{radial_distribution.pdf}
	}
    \caption{The radial distributions of UDGs (\textit{left}) and UPGs (\textit{right}). We subtract the background contamination (shown in teal) and correct for completeness in each radial distance bin (shown in red). We fit the projected NFW and Einasto profiles to the radial distributions and find good fits for both profiles. The radial distributions of UDGs and UPGs are similar in shape. The best-fit NFW concentrations is consistent with a MW-mass halo, whereas the best-fit Einasto profiles have smaller concentration than MW-mass halos.}
    \label{fig:radial_distribution}
\end{figure*}

\subsection{Quenched fraction}\label{sec:quench}
Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched. Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.

UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields, however there are one or two red UDGs in fields. It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up? 3) how are they quenched? what's the correlation between quenching and puffing.

We compare with SAGA quenched fraction (Mao) and ELVES (Carlsten, Greene in prep).

@@

\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.
\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.

When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish? because we don't know about their mass-size.

The mass-size doesn't depend on color (carlsten). The quenched fraction also doesn't depend on size. Reflect on Danieli\&vD mass-size slice paper.

SAGA misses a fraction of red faint galaxies in their intial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
	}
    \caption{Caption}
    \label{fig:qfrac_dist2host}
\end{figure*}

@@

\section{Discussion and Conclusion}
TODO: make data products (catalogs, fake UDGs, website for their images, etc.)

\subsection{A better definition for diffuse galaxies}

discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).

Scenarios:
1. violent environmental effects: radial orbits, back-splash both explain large size and quenching. But according to Bernavidis et al, the quenched fraction drops with increasing mass.

@@

\section*{Acknowledgment}
JL is grateful for discussions with Meng Gu. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.

@@

\vspace{1em}
\software{\href{http://www.numpy.org}{\code{NumPy}} \citep{Numpy},
          \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy}, \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
        %   \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
          \href{https://bdiemer.bitbucket.io/colossus/index.html}{\code{Colossus}} \citep{Colossus},
          \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}, \href{https://github.com/dr-guangtou/unagi}{\code{unagi}}.
          }

@@

\section{Spergel profiles}\label{ap:spergel}
\begin{figure*}[htbp!]
	\vbox{ 
		\centering
		\includegraphics[width=0.75\linewidth]{spergel_sersic_calib.pdf}
	}
    \caption{The correspondence between the \sersic{} profile \eqref{eq:sersic} and the Spergel profile \eqref{eq:spergel}. We fit a Spergel profile to \sersic{} while fixing the total luminosity and half-light radius. The left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$. In the right panel, two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) are shown. Spergel profile approximates \sersic{} well for small \sersic{} indices.  
    }
    \label{fig:spgl_calib}
\end{figure*}

@@

To study the correspondence between \sersic{} and Spergel profiles, we generate \sersic{} profiles with different \sersic{} indices, and try to fit Spergel profiles to \sersic{} ones. The \sersic{} index ranges from $n=0.5$ to $n=4.5$, and both profiles are normalized using $r_e$. For each \sersic{} profile, we calculate the total luminosity $L_0$ according to \eqref{eq:sersic_lum} and plug it into the Spergel profile \eqref{eq:spergel} as a fixed value. Therefore, only the Spergel index $\nu$ is allowed to vary during the fitting. The best-fit Spergel index $\nu$ as a function of \sersic{} index $n$ is shown in the left panel of Figure \ref{fig:spgl_calib}. As two examples, we show two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) in the right panel. A Spergel profile with $\nu=0.5$ is exactly an exponential profile with $n=1$. The de Vaucouleurs profile \citep{deVaucouleurs1948} with $n=4$ can be approximated by a Spergel profile with $\nu=-0.74$.

@@

% \section{Measurement Error}\label{ap:meas_error}

% We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

% vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)

% Remember to ref SMUDGES papers here.
